Positional entropy, conditional entropy and mutual information in English CHILDES corpora

### 2018-09-18 english_unigram&ce&mi.Rmd
bootstrapping slope analysis

Compute Providence Corpus Estimates
```{r calc_pos_entropy}
get_entropies <- function(role, sen_length, utterances) {

>>>>

bootstrap entropy slopes
```{r }
lengths <- brown_utterances %>%
  filter(speaker_role  != "Target_Child") %>%
  mutate(length = str_count(stem, " ") + 1) %>%

tokens <- lengths %>% 
  filter(length >= 3) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, stem) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    summarise(n = n())

start_slope <- function(df) {

 df %>%
    filter(word_order %in% c(1,2)) %>%
    sample_frac(1, replace = T) %>%
    group_by(length, word_order) %>%
    summarise(entropy = entropy(n, unit = "log2")) %>%
    spread(word_order, entropy) %>%
    ungroup() %>%
    mutate(diff = `2` - `1`) %>%
    summarise(diff = mean(diff)) %>%
    pull(diff)

end_slope <- function(df) {

 df %>%
    ungroup() %>%
    mutate(word_order = if_else(word_order == length, 2,
                                if_else(word_order == length -1 , 1,
                                        0))) %>%
    filter(word_order > 0) %>%
    group_by(length, word_order) %>%
    sample_frac(1, replace = T) %>%
    group_by(length, word_order) %>%
    summarise(entropy = entropy(n, unit = "log2")) %>%
    spread(word_order, entropy) %>%
    ungroup() %>%
    mutate(diff = `2` - `1`) %>%
    summarise(diff = mean(diff)) %>%
    pull(diff)

start_time <- Sys.time()
samples <- replicate(1000, end_slope(tokens))  %>%
  as_data_frame()
end_time <- Sys.time()

samples %>%
  summarise(mean = mean(value), ci_upper = quantile(value, .975), 
            ci_lower = quantile(value, .025))

```
Compute Providence Corpus Estimates
```{r calc_pos_entropy}
get_entropies <- function(role, sen_length, utterances) {
